Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-19 sections/02-notation.tex
Small corrections
Update on Overleaf.

The trending detection of time series, as motivated in the introduction, is fundamentally interesting for evaluating and comparing methods from three areas: measurement technology, forecasting, and nowcasting.
This paper relates to numerical data. \todo{Hängt irgendwie in der Luft}
\todo{Überleitung, dass jetzt die einzelnen vorgestellt werden}

Measurement aims to obtain accurate and reliable data about the current state of a system.
Often, the question is how to compare one method of measurement of a variable with another.
For this purpose, measured values can be recorded with the two measurement methods to be compared (one can be the gold standard) for the same variable in the same period of time.
The measured values for a measurement method are then available in a time series form, e.g., can be noted with $(x_t)^T_{t=0}$. \todo{Fehlt da nicht noch $y$?}
To detect the systematic difference between the two methods, a paired t-test can be performed on the pairwise difference of the two series of measurements to test the null hypothesis that the true mean difference is zero\cite{watson2010method}.
In addition, various indices such as the interclass correlation coefficient or Lin's concordance correlation, which were originally introduced as a modification of the Pearson correlation, have been proposed in practice to check the reproducibility of the measurement or to compare different measurement methods (cf. \cite{lawrence1989concordance,koo2016guideline,}). \todo{Andere Zitierfunktion}
Furthermore, graphical tools were developed, such as the Bland-Altman diagram, which visualizes the differences between the methods in relation to their mean value (cf. \cite{bland1986statistical}).

@@

\todo[inline]{Überleitung}
Nowcasting (also short-term forecasting), on the other hand, has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (cf. \cite{browning1989nowcasting,schmid2019nowcasting}).
Nowcasting focuses on predictions for the present, the immediate future, and the recent past and is now being used in other fields, such as the economy\todo{economics?}, where important statistics on the current economic situation are available only after a considerable time lag (cf. \cite{banbura2013now}), and in medicine, where epidemic nowcasting is used during an ongoing epidemic outbreak to assess the current situation, taking into account the main pathogenic, epidemiological, clinical and socio-behavioral factors (cf. \cite{wu2021nowcasting}). \todo{sehr langer Satz}
Applications of nowcasting methods for econometrics can be found here in \cite{giannone2006nowcasting,fornaro2020nowcasting,bok2018macroeconomic} or for predictions of epidemic development here in \cite{johansson2014nowcasting,gunther2021nowcasting,birrell2021real}. \todo{Satz klingt noch nicht so ganz rund}
When predicting values in the present, it is usual that the true values of the recent past are not available, so only an estimate of these values is provided by the nowcast.\todo{Vielleicht noch etwas konkreter machen}
Using the notation for forecasting above, this means that a prediction value $x_{t,\tau}$ also exiertits \todo{word?} for $\tau$ less than or equal to $t$.
Similar to forecasting, nowcasters are often evaluated and compared in the literature on the basis of performance measures such as the root mean absolute error (cf. \cite{gunther2021nowcasting}).

>>>>

The trending detection of time series, as motivated in the introduction, is fundamentally interesting for evaluating and comparing methods from three areas: measurement technology, forecasting, and nowcasting.
This paper relates to numerical data. \todo{Hängt irgendwie in der Luft} \unsure{Müsste es nicht auch ausschließlich um wiederholte Messungen gehen?}
\todo{Überleitung, dass jetzt die einzelnen vorgestellt werden}

Measurement aims to obtain accurate and reliable data about the current state of a system.
Often, the question is how to compare one method of measurement of a variable with another.
For this purpose, measured values can be recorded with the two measurement methods to be compared (one can be the gold standard) for the same variable in the same period of time.
The measured values for a measurement method are then available in a time series form, e.g., can be noted with $(x_t)^T_{t=0}$. \todo{Fehlt da nicht noch $y$?}
To detect the systematic difference between the two methods, a paired t-test can be performed on the pairwise difference of the two series of measurements to test the null hypothesis that the true mean difference is zero\cite{watson2010method}.
In addition, various indices such as the interclass correlation coefficient or Lin's concordance correlation, which were originally introduced as a modification of the Pearson correlation, have been proposed in practice to check the reproducibility of the measurement or to compare different measurement methods (\cite{lawrence1989concordance,koo2016guideline,}). \todo{Andere Zitierfunktion}
Furthermore, graphical tools were developed, such as the Bland-Altman diagram, which visualizes the differences between the methods in relation to their mean value (\cite{bland1986statistical}).

@@

\todo[inline]{Überleitung}
Nowcasting (also short-term forecasting), on the other hand, has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}).
Nowcasting focuses on predictions for the present, the immediate future, and the recent past and is now being used in other fields, such as the economy\todo{economics?}, where important statistics on the current economic situation are available only after a considerable time lag (\cite{banbura2013now}), and in medicine, where epidemic nowcasting is used during an ongoing epidemic outbreak to assess the current situation, taking into account the main pathogenic, epidemiological, clinical and socio-behavioral factors (\cite{wu2021nowcasting}). \todo{sehr langer Satz}
Applications of nowcasting methods for econometrics can be found here in \cite{giannone2006nowcasting,fornaro2020nowcasting,bok2018macroeconomic} or for predictions of epidemic development here in \cite{johansson2014nowcasting,gunther2021nowcasting,birrell2021real}. \todo{Satz klingt noch nicht so ganz rund}
When predicting values in the present, it is usual that the true values of the recent past are not available, so only an estimate of these values is provided by the nowcast.\todo{Vielleicht noch etwas konkreter machen}
Using the notation for forecasting above, this means that a prediction value $x_{t,\tau}$ also exiertits \todo{word?} for $\tau$ less than or equal to $t$.
Similar to forecasting, nowcasters are often evaluated and compared in the literature on the basis of performance measures such as the root mean absolute error (\cite{gunther2021nowcasting}).
